\item \points{35} {\bf Semi-supervised EM}

\def\zsi{z^{(i)}}
\def\xsi{x^{(i)}}

Expectation Maximization (EM) is a classical algorithm for unsupervised learning (\emph{i.e.,} learning with hidden or latent variables). In this problem we will explore one of the ways in which EM algorithm can be adapted to the semi-supervised setting, where we have some labeled examples along with unlabeled examples.

In the standard unsupervised setting, we have $\nexp \in \mathbb{N}$ unlabeled examples $\{x^{(1)},\ldots,x^{(\nexp)}\}$. We wish to learn the parameters of $p(x,z;\theta)$ from the data, but $\zsi$'s are not observed. The classical EM algorithm is designed for this very purpose, where we maximize the intractable $p(x;\theta)$ indirectly by iteratively performing the E-step and M-step, each time maximizing a tractable lower bound of $p(x;\theta)$. Our objective can be concretely written as:

\begin{align*}
    \ell_{\text{unsup}}(\theta) &= \sum_{i=1}^\nexp \log p(\xsi;\theta) \\
    &= \sum_{i=1}^\nexp \log \sum_{\zsi} p(\xsi,\zsi;\theta)
\end{align*}


Now, we will attempt to construct an extension of EM to the semi-supervised setting. Let us suppose we have an \emph{additional} $\tilde{\nexp} \in \mathbb{N}$ labeled examples $\{(\tilde{x}^{(1)},\tilde{z}^{(1)}),\ldots,(\tilde{x}^{(\tilde{\nexp})},\tilde{z}^{(\tilde{\nexp})})\}$ where both $x$ and $z$ are observed. We want to simultaneously maximize the marginal likelihood of the parameters using the unlabeled examples, and full likelihood of the parameters using the labeled examples, by optimizing their weighted sum (with some hyperparameter $\alpha$). More concretely, our semi-supervised objective $\ell_\text{semi-sup}(\theta)$ can be written as:
%
\begin{align*}
    \ell_\text{sup}(\theta) &= \sum_{i=1}^{\tilde{\nexp}} \log p(\tilde{x}^{(i)},\tilde{z}^{(i)};\theta) \\
    \ell_{\text{semi-sup}}(\theta) &= \ell_\text{unsup}(\theta) + \alpha \ell_\text{sup}(\theta)
\end{align*}
%
We can derive the EM steps for the semi-supervised setting using the same approach and steps as before. You are \emph{strongly encouraged} to show to yourself (no need to include in the write-up) that we end up with:

\subsubsection*{E-step (semi-supervised)}

For each $i \in \{1,\ldots,\nexp\}$, set
\begin{align*}
    Q_i^{(t)}(\zsi) := p(\zsi|\xsi;\theta^{(t)})
\end{align*}

\subsubsection*{M-step (semi-supervised)}

\begin{align*}
    \theta^{(t+1)} &:= \arg\max_\theta\left[ \sum_{i=1}^\nexp\left( \sum_{\zsi} Q^{(t)}_i(\zsi) \log \frac{ p(\xsi, \zsi;\theta) }{ Q^{(t)}_i(\zsi)}\right)  + \alpha \left(\sum_{i=1}^{\tilde{\nexp}} \log p(\tilde{x}^{(i)},\tilde{z}^{(i)};\theta)\right)\right]
\end{align*}

\begin{enumerate}
  \input{semi_supervised_em/01-convergence}
\ifnum\solutions=1 {
  \input{semi_supervised_em/01-convergence-sol}
} \fi

\end{enumerate}


\subsubsection*{Semi-supervised GMM}
Now we will revisit the Gaussian Mixture Model (GMM), to apply our semi-supervised EM algorithm. Let us consider a scenario where data is generated from $k \in \mathbb{N}$ Gaussian distributions, with unknown means $\mu_j \in \R^\di$ and covariances $\Sigma_j \in \mathbb{S}_+^\di$ where $j \in \{1,\ldots,k\}$. We have $\nexp$ data points $\xsi \in \R^\di, i \in \{1,\ldots,\nexp\}$, and each data point has a corresponding latent (hidden/unknown) variable $\zsi \in \{1,\ldots,k\}$ indicating which distribution $\xsi$ belongs to. Specifically, $\zsi \sim \text{Multinomial}(\phi)$, such that $\sum_{j=1}^k\phi_j = 1$ and $\phi_j \ge 0$ for all $j$, and $\xsi|\zsi \sim \mathcal{N}\left(\mu_{\zsi}, \Sigma_{\zsi}\right)$ i.i.d. So, $\mu$, $\Sigma$, and $\phi$ are the model parameters.

We also have additional $\tilde{\nexp}$ data points $\tilde{x}^{(i)} \in \R^\di, i \in \{1,\ldots,\tilde{\nexp}\}$, and an associated \emph{observed} variable $\tilde{z}^{(i)} \in \{1,\ldots,k\}$ indicating the distribution $\tilde{x}^{(i)}$ belongs to. Note that $\tilde{z}^{(i)}$ are known constants (in contrast to $\zsi$ which are unknown \emph{random} variables). As before, we assume $\tilde{x}^{(i)}|\tilde{z}^{(i)} \sim \mathcal{N}\left(\mu_{\tilde{z}^{(i)}}, \Sigma_{\tilde{z}^{(i)}}\right)$ i.i.d.


In summary we have $\nexp$ + $\tilde{\nexp}$ examples, of which $\nexp$ are unlabeled data points $x$'s with unobserved $z$'s, and $\tilde{\nexp}$ are labeled data points $\tilde{x}^{(i)}$ with corresponding observed labels $\tilde{z}^{(i)}$. The traditional EM algorithm is designed to take only the $\nexp$ unlabeled examples as input, and learn the model parameters $\mu$, $\Sigma$, and $\phi$.


Our task now will be to apply the semi-supervised EM algorithm to GMMs in order to also leverage the additional $\tilde{\nexp}$ labeled examples, and come up with semi-supervised E-step and M-step update rules specific to GMMs. Whenever required, you can cite the lecture notes for derivations and steps.


\begin{enumerate}
  \setcounter{enumii}{1}
  \input{semi_supervised_em/02-e-step}
\ifnum\solutions=1 {
  \input{semi_supervised_em/02-e-step-sol}
} \fi

  \input{semi_supervised_em/03-m-step}
\ifnum\solutions=1 {
  \input{semi_supervised_em/03-m-step-sol}
} \fi


  \input{semi_supervised_em/04-impl-unsupervised}
\ifnum\solutions=1 {
  \input{semi_supervised_em/04-impl-unsupervised-sol}
} \fi

  \input{semi_supervised_em/05-impl-semi-supervised}
\ifnum\solutions=1 {
  \input{semi_supervised_em/05-impl-semi-supervised-sol}
} \fi

  \input{semi_supervised_em/06-comparison}
\ifnum\solutions=1 {
  \input{semi_supervised_em/06-comparison-sol}
} \fi

\end{enumerate}
