\item \points{22} {\bf Spam classification}

In this problem, we will use the naive Bayes algorithm and an SVM to
build a spam classifier.

In recent years, spam on electronic media has been a growing concern.  Here, we'll build a classifier to distinguish
between real messages, and spam messages. For this class, we will be building a classifier to detect SMS spam messages. We will be using an SMS spam dataset developed by Tiago A. Almedia and José María Gómez Hidalgo which is publicly available on \url{http://www.dt.fee.unicamp.br/~tiago/smsspamcollection} \footnote{Almeida, T.A., Gómez Hidalgo, J.M., Yamakami, A. Contributions to the Study of SMS Spam Filtering: New Collection and Results.  Proceedings of the 2011 ACM Symposium on Document Engineering (DOCENG'11), Mountain View, CA, USA, 2011.}

We have split this dataset into training and testing sets and have included them in this assignment as \texttt{src/spam/spam\_train.tsv} and \texttt{src/spam/spam\_test.tsv}. See \texttt{src/spam/spam\_readme.txt} for more details about this dataset. Please refrain from redistributing these dataset files. The goal of this assignment is to build a classifier from scratch that can tell the difference the spam and non-spam messages using the text of the SMS message.

\begin{enumerate}
  \input{spam/01-input-processing}
  \ifnum\solutions=1 {
    \input{spam/01-input-processing-sol}
  } \fi

  \input{spam/02-naive-bayes}
  \ifnum\solutions=1 {
    \input{spam/02-naive-bayes-sol}
  } \fi

  \input{spam/03-five-best}
  \ifnum\solutions=1 {
    \input{spam/03-five-best-sol}
  } \fi

  \input{spam/04-svm}
  \ifnum\solutions=1 {
    \input{spam/04-svm-sol}
  } \fi
\end{enumerate}
